---
title: "hw06: More Cowbell on the Web Scraping"
author: 'STAT 385, Spring 2018'
date: 'Due: Monday, April 9th, 2018 at 11:59 PM'
output:
  html_document:
    theme: readable
    toc: yes
---

# Overview 

Please see the [homework policy](http://stat385.thecoatlessprofessor.com/homework-policy/)
for detailed instructions and some grading notes. Failure to follow instructions
will result in point reductions. In particular, make sure to commit each 
exercise as you complete them. 

> "Our greatest glory is not in never falling, but in rising every time we fall."
> 
> — Confucius

## Objectives 

The objectives behind this homework assignment are as follows:

- Navigate semi-structured HTML websites;
- Extract different tags and attribute values from a web page;
- Save and load a file dynamically into an RMarkdown document;
- Identifying, extracting, and replacing patterns in a string with regular expressions;
- Manipulating strings;
- Coercing data types;
- Creating and interpreting graphs

## Grading

The rubric CAs will use to grade this assignment is:

| Task                                                   | pts |
|:-------------------------------------------------------|----:|
| Link to GitHub Repository   	                         | 2   |
| At least one commit per exercise (more is better!)     | 5   |
| Commit messages that describe what changed	           | 5   |
| Ceci n'est pas une pipe                                | 8   |
| A Periodic Dose of Romance, Sarcasm, Math, and Language| 12  |
| Living the La Vida Loca                                | 28  |
| Web Scrapper Jo'                                       | 12  |
| Total                                                  | 72  |

## Note on Regular Expressions

For this homework assignment, it is _strongly_ recommend that you consult both
the [Web Scraping](http://stat385.thecoatlessprofessor.com/lectures/16-web-scraping/16-web-scraping.pdf)
and 
[Regular Expression lecture slides](http://stat385.thecoatlessprofessor.com/lectures/15-regular-expressions/15-regular-expressions.pdf)
lectures. Other resources that may be helpful include: 

- [`rvest` Vignette: Selectorgadget](https://cran.r-project.org/web/packages/rvest/vignettes/selectorgadget.html)
- [SelectorGadget](http://selectorgadget.com/)

## Package usage

For this homework assignment, you may only use the following _R_ packages:

```{r}
pkg_list = c("ggplot2", "stringr", "rvest", "tidyr", "dplyr")
mia_pkgs = pkg_list[!(pkg_list %in% installed.packages()[,"Package"])]
if(length(mia_pkgs) > 0) install.packages(mia_pkgs)
loaded_pkgs = lapply(pkg_list, require, character.only=TRUE)
```

-----

## (12 Points) Exercise 0: We Live in a Beautiful GitHub World!

**NB** When cloning this repository, you should opt-in to using the
"base" template of the STAT 385 Workspace on RStudio Cloud.

- **[2 Points] (a)** Place a link to your `hw06` GitHub repository here.

[Kevin's link to hw06 GitHup repository](https://github.com/stat385-sp2018/hw06-KevinWong2)

- **[5 Points] (b)** Commit every exercise as you finish them. 
- **[5 Points] (c)** Make each commit message _meaningful_. 
    - The bare minimum for a "meaningful" commit is a length of 15 characters.
    - Inside the commit message, please make sure to appropriately describe 
      what is happening.
        - e.g. stating "Exercise 3" or "Ex3" is **not** sufficient.
        - Provide details on the state, e.g. "Finished exercise 3" or
        "Checking in a work in progress attempt on iterating over hockey data."
          
## (8 Points) Exercise 1: Ceci n'est pas une pipe.

- **[2 points] (a)** Explain what is happening behind the piped statements in
  the following pipeline:
    - _Hint:_ The `lm()` function performs a linear regression with `y ~ x`.
 
```{r, eval = FALSE}
data %>%
    subset(livelihood >= 2000) %>%
    subset(select = c("livelihood", "height")) %>%
    lm(livelihood ~ height, data = .)
```

- The dataset named `data` is being subsetted on only those observations that have the `livelihood` variable of a value of at least 2000. Then, `data` is being subsetted again and only including the variables `livelihood` and `height`. Lastly, we are creating a linear model using this updated version of `data`, and the linear model is `livelihood` predicted by `height`.

- **[2 points] (b)** Transform the following _embedded function call_ into
  a series of piped statements.
    - _Hint:_ To select a variable inside a pipe using Base R use: `data %>% .[["variable"]]`
  
```{r}
library("magrittr")

# Embedded Function Calls
mean(head(subset(iris, Sepal.Length > mean(Sepal.Length)))[["Sepal.Length"]])
```

```{r pipe-transformation}
iris %>%
  subset(Sepal.Length > mean(Sepal.Length)) %>%
  .[['Sepal.Length']] %>%
  head() %>%
  mean()
```

- **[4 points] (c)** Create a piping story that shows a multi-step problem that
  can be found in real-world. For inspiration, recall either 
  [Hadley Wickham's Bunny Foo-Foo]() or the [Starbucks Mobile Order]().
      - Have at least four different steps to the story.

```{r making-own-story, eval = FALSE}
plugin("television") %>%  #Step 1
  turnon() %>% #Step 2
  changeChannel(channel = "ESPN") %>% #Step 3
  sitdown(location = "couch") %>% #Step 4
  watch("Illini") #Step 5
```

## (12 Points) Exercise 2: A Periodic Dose of Romance, Sarcasm, Math, and Language

Behind this exercise, the goal is to highlight the ability to download a file
from a website and include it within an _RMarkdown_ document. The file may _change_
each day and, thus, the document is able to "automatically" update itself. As 
a result, we have provided a "sample" of what was present when the homework
was initially released.

**Note:** To avoid excessive retrievals, please add to the _R_ code chunk that
reads in the data the chunk option of `cache = TRUE`. So, the code is executed
only once unless its contents change.

- **[2 points] (a)** Download and read into _R_ the **HTML** for <http://xkcd.com/>.
    - **Note:** This is the main URL. Do _not_ hard code a URL with a specific
      comic number. Examples given below correspond to a _specific_ number for
      illustrative purposes only, but the solution rests in being able to 
      retrieve a comic dynamically.

```{r read-xkcd, cache = TRUE}
url_ex2 = "http://xkcd.com/"
xkcd_website = read_html(url_ex2)
```

-  **[2 points] (b)** Extract the URL for the daily comic image and properly format it. 
    - The comic image is the main image shown on the webpage.
    - _Hint:_ You may need to _unselect_ another image on the page (e.g. XKCD's logo)
      to obtain the appropriate selector. 
    - _Example:_ [On April 2nd](https://xkcd.com/1975/), the daily comic image URL was
      `//imgs.xkcd.com/comics/right_click.png`
    - **Note:** This is URL is missing the _scheme_ at the front-most portion 
      of it. Make sure to _append_ to the extract value the appropriate scheme.

```{r extract-url}
url_ex2_comic_image =
  xkcd_website %>%
    html_node(css = "#comic img") %>%
    str_extract(pattern = "//.*") %>%
    str_replace(pattern = "\".*", replacement = "")

url_ex2_comic_image
```

-  **[2 points] (c)** Extract the filename for the comic in the URL using regex
    and store it in `comic_filename`.
    - _Example:_[On April 2nd](https://xkcd.com/1975/), name of the image contained
      within the comic image URL was: **right_click.png**

```{r extracting-file-name}
comic_filename = 
  url_ex2_comic_image %>%
    str_extract(pattern = "comics.*") %>%
    str_replace(pattern = "comics/", replacement = "")

comic_filename
```

-  **[2 points] (d)** Extract the `title` attribute value of the daily comic image.
    - **Note:** This attribute is only visible if the mouse is over the comic
    image on the website. This is **not** the name of the comic as it is displayed
    on the website.
    - _Example:_ [On April 2nd](https://xkcd.com/1975/), the `title` attribute value
    on the daily comic image was: 
    
> Right-click or long press (where supported) to save!

```{r extract-title}
comic_title =
  xkcd_website %>% 
    html_nodes("#comic img") %>%
    str_extract(pattern = "title.*") %>%
    str_replace_all(pattern = "\\\\|\"|title=| alt=.*", replacement = "")

comic_title
```

- **[2 points] (e)** Download the comic image to disk using `download.file(url, comic_filename)`

```{r downloading-comic-image}
download.file(url_ex2, comic_filename)
```

- **[2 points] (f)** Dynamically include inside the RMarkdown file the comic 
  picture, e.g. `comic_filename`, and the mouse over text, e.g. `title` attribute value.

_Hint:_ How do you evaluate inline R code in RMarkdown (See 
[Lecture 02: Literate Programming](http://stat385.thecoatlessprofessor.com/lectures/02-literate-programming/02-literate-programming.pdf#page=46))?
How can this be used to dynamically set an image's name? e.g. `![dynamic code for comic title](dynamic code for URL)` 

![`r comic_title`](`r comic_filename`)

## (28 Points) Exercise 3: Living the Vida Loca

**Note:** To avoid excessive retrievals, please add to the _R_ code chunk that
reads in the data the chunk option of `cache = TRUE`. So, the code is executed
only once unless its contents change.

- **[2 points] (a)** Download and read into _R_ the **HTML** for <https://chambana.craigslist.org/d/apts-housing-for-rent/search/apa>.
    - This contains the current housing prices for renting an apartment in the
    Champaign-Urbana Area from Craiglist.

```{r read-chambana, cache = TRUE}
url_ex3 = "https://chambana.craigslist.org/d/apts-housing-for-rent/search/apa"
champaign_website = read_html(url_ex3)
```

- **[2 points] (b)** Extract the date the ad was added to Craigslist
    - The date added is list to the _right_ of the "star" icon.

```{r extract-date}
ex3_dates = 
  champaign_website %>%
    html_nodes(css = ".result-date") %>%
    str_extract(pattern = "[[:digit:]]{4}-[[:digit:]]{2}-[[:digit:]]{2}")

head(ex3_dates)
```

- **[2 points] (c)** Extract the text describing the listing
    - The text describing the listing is to the _right_ of the date.

```{r extract-listing-text}
ex3_text =
  champaign_website %>%
    html_nodes(css = ".result-title") %>%
    str_extract(pattern = "hdrlnk.*") %>%
    str_replace_all(pattern = "hdrlnk\\\">|</a>", replacement = "")

head(ex3_text)
```

- **[2 points] (d)** Extract location of the apartments and remove the `()` around
    the data.
    - The text describing the listing is to the _right_ of the date.
    - _Hint:_ Use the find and replace ability of regex to remove the `()`.

```{r extract-location}
ex3_addresses = 
  champaign_website %>%
    html_nodes(css = ".result-hood") %>%
    str_extract(pattern = "\\(.*\\)") %>%
    str_replace_all(pattern = "[()]", replacement = "")

head(ex3_addresses)
```

- **[4 points] (e)** Create four variables that act as indicators as to whether
    the apartment is in Champaign, Urbana, Savoy, or "Other (e.g. not listed)".
    - There should be four vectors with either `TRUE` or `FALSE` depending on 
      whether the location of the apartment contains the aforementioned towns.
    - _Hint:_ You will likely need to use `regex()` with
    `ignore.case = TRUE` to ensure appropriate matching of the city names.

```{r city-table}
ex3_addresses =
  champaign_website %>%
    html_nodes(css = ".result-hood") %>%
    str_extract(pattern = "\\(.*\\)") %>%
    str_replace_all(pattern = "[()]", replacement = "")
ex3_location_cham  = str_detect(string = ex3_addresses, pattern = "Champaign")
ex3_location_urb   = str_detect(string = ex3_addresses, pattern = "Urbana")
ex3_location_sav   = str_detect(string = ex3_addresses, pattern = "Savoy")
ex3_location_other = ifelse(ex3_location_cham | ex3_location_urb | ex3_location_sav == TRUE, FALSE, TRUE)

ex3_location_table = data.frame(
  ex3_location_cham  = ex3_location_cham,
  ex3_location_urb   = ex3_location_urb,
  ex3_location_sav   = ex3_location_sav,
  ex3_location_other = ex3_location_other
)

colnames(ex3_location_table) = c("Champaign", "Urbana", "Savoy", "Other")
head(ex3_location_table)
```

- **[4 points] (f)** Extract the _price_ per month from each listing and convert
    the value from a character to a **numeric**
    - The price is given in to the _right_ of the listing title.
    - _Hints:_ Do not use the price in the upper left corner. Before converting
     from a character to an numerics, remove the dollar sign (`$`).

```{r extract-price-per-month}
ex3_price =
  champaign_website %>%
    html_nodes(css = ".result-price") %>%
    str_extract(pattern = "\\$.*<") %>%
    str_replace_all(pattern = "[$<]", replacement = "") %>%
    as.numeric()

head(ex3_price)
```

- **[6 points] (g)** Extract the features of the apartment
    - e.g. `4br` denotes 4 bedrooms and should be simplified to `4` integer
    - e.g. `1325ft2` denotes 1325 square ft of space and should be simplified to
      `1325` numeric.
    - This is typically denoted `4br - 1325ft2` or is sometimes given as `2br -`.
    - Do _not_ worry about whether a listing is missing information.

```{r extract-features}
ex3_bedrooms = 
  champaign_website %>%
    html_nodes(css = ".housing") %>%
    str_extract(pattern = "[[:digit:]].*br") %>%
    str_replace(pattern = "br", replacement = "") %>%
    as.integer()

ex3_sqft = 
  champaign_website %>%
    html_nodes(css = ".housing") %>%
    str_extract(pattern = "[[:digit:]].*ft") %>%
    str_replace(pattern = "ft", replacement = "") %>%
    as.numeric()

head(ex3_bedrooms)
head(ex3_sqft)
```

- **[6 points] (i)** Create three separate plots that show:
    - the distribution of rent (numeric);
    - the amount of bedrooms in a house (discrete);
    - the overall amount of square footage (numeric).

```{r ex3i-plots}
ggplot(mapping = aes(x = ex3_price)) + 
  geom_histogram(fill = "darkblue", color = "orange") +  
    labs(x = "Rent Price")
ggplot(mapping = aes(x = ex3_bedrooms)) + 
  geom_bar(fill = "darkblue", color = "orange") +  
    labs(x = "Amount of Bed Rooms")
ggplot(mapping = aes(x = ex3_sqft)) + 
  geom_histogram(fill = "darkblue", color = "orange") +  
    labs(x = "Square Footage of Home")
```

## (12 Points) Exercise 4: Web Scrapper Jo'

**Note:** To avoid excessive retrievals, please add to the _R_ code chunk that
reads in the data the chunk option of `cache = TRUE`. So, the code is executed
only once unless its contents change.

- Specify the name of the website that you wish to scrap.
  Post it on our [GitHub Discussion Forum](https://github.com/stat385-sp2018/disc/issues/101). **Everyone must have their own unique website.**
- Verify you can access the data on the website _before_ claiming it. 
    - e.g. Make sure a selector returns a value. If it doesn't, then this likely means the page has _JavaScript_ on it. JavaScript unfortunately is not captured correctly when `rvest` reads in the HTML.
- The website must contain:
    - **[4 points]** A collection of elements (e.g. titles of multiple posts)
    - **[4 points]** Attribute information on elements (e.g. hrefs)
    - **[4 points]** A table
- Do not scrap any data on: imdb.com, rottentomatos.com, slashdot.org,
xkcd.com, illinois.edu, news.google.com, wunderground.com, craigslist.com, 
or any website we scraped in class...

```{r illinois-fighting-illini-website-read-html, cache = TRUE}
url_ex4 = "http://fightingillini.com/staff.aspx"
ill_website = read_html(url_ex4)
```

### Collection of Elements
```{r illinois-staff}
ill_staff =
  ill_website %>%
    html_nodes(css = ".staff_dgrd_fullname") %>%
    str_extract(pattern = "[[:digit:]].*") %>%
    str_replace_all(pattern = "[[:digit:]]|\\\\|\"|>|</a>.*", replacement = "")

head(ill_staff)
```

### Attribute Information on Elements
```{r illinois-html-attributes}
ill_info_attrs = 
  ill_website %>%
    html_nodes(css = ".staff_address_info table") %>%
    html_nodes(css = "a") %>%
    html_attr(name = "href")

ill_staff_attrs = 
  ill_website %>%
    html_nodes(css = ".staff_dgrd_fullname") %>%
    html_nodes(css = "a") %>%
    html_attr(name = "href")

head(ill_info_attrs)
head(ill_staff_attrs)
```

### Making a Table

```{r illinois-locations}
ill_locations =
  ill_website %>%
    html_nodes(css = ".staff_address_info table") %>%
    html_nodes(css = "td p") %>%
    str_extract(pattern = "strong>.*") %>%
    str_replace_all(pattern = "strong>|</strong><br>|<br>", replacement = "")
```

```{r illinois-office-phone-numbers}
ill_phone_numbers =
  ill_website %>%
    html_nodes(css = "td p") %>%
    str_extract(pattern = "[[:digit:]]{3}-[[:digit:]]{3}-[[:digit:]]{4}")
```

```{r illinois-office-cities}
ill_cities = 
  ill_website %>%
    html_nodes(css = "td p") %>%
    str_extract(pattern = ".* [[:digit:]]{5}") %>%
    str_replace_all(pattern = "\\t", replacement = "") %>%
    str_extract(pattern = ".*,") %>%
    str_replace(pattern = "[[:punct:]]", replacement = "")
```

```{r illinois-office-states}
ill_states = 
  ill_website %>%
    html_nodes(css = "td p") %>%
    str_extract(pattern = ".* [[:digit:]]{5}") %>%
    str_replace_all(pattern = "\\t", replacement = "") %>%
    str_extract(pattern = ",.*") %>%
    str_replace(pattern = ", ", replacement = "") %>%
    str_extract(pattern = "[A-Z]{2}")
```

```{r illinois-office-zip-codes}
ill_zip_codes = 
  ill_website %>%
    html_nodes(css = "td p") %>%
    str_extract(pattern = "[[:digit:]]{5}")
```

```{r illinois-office-table}
ill_office_table =
  data.frame(
    ill_locations     = ill_locations,
    ill_phone_numbers = ill_phone_numbers,
    ill_cities        = ill_cities,
    ill_states        = ill_states,
    ill_zip_codes     = ill_zip_codes
  )

colnames(ill_office_table) = c("Location", "Phone Number", "City", "State", "Zip Code")
ill_office_table
#GO ILLINI!!!!!!!!
```

