---
title: "Kevin Wong - Korean"
output:
  html_document:
    toc: no
---

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(ggplot2)
library(kableExtra)
library(knitr)
library(lubridate)
library(rlang)
library(shiny)
library(shinydashboard)
library(stringr)
library(tidyverse)
```

```{r echo = FALSE}
Update_Date = as.Date("2-1-2025", format = "%m-%d-%Y")
Today_Date = Sys.Date()
```

<style type="text/css">

<!--
body .main-container {
  width: 900px !important;
	max-width: 1080px !important;
}
-->

.r33m_vid {
   font-family: Tahoma;
   color: black;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

.korean {
  font-family: "Lucida Grande";
  font-size: 18px;
  color: white;
}

</style>


<h1>Languages</h1>

<p class="last-updated">
Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`
</p>

***

<p class="korean">
안녕하세요! 저는 케빈입니다. 감사합니다.
</p>

***

<p class="last-updated">
Please use my Shiny app to practice Korean and test your knowledge.
</p>

<iframe height="600" width="100%" frameborder="yes" src="https://kevinjameswong.shinyapps.io/korean/">
</iframe>



```{r echo = FALSE, eval = FALSE}
Silent ㅌ = 4
Silent ㅅ = 4
Silent ㅈ = 4
Silent ㅂ = 4



Silent ㄹ = 3

if ㄹ = 3,  ㅂ = 4, the ㅂ is silent. yal
if ㅂ = 3,  ㅅ = 4, the ㅅ is silent. eop
if ㄹ = 3,  ㅅ = 4, the ㅅ is silent. gol
```





