---
title: "Kevin Wong - Running Data"
output:
  html_document:
    toc: yes
---

<style>
body {
  background-color: #FF8200;
}
</style>

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(lubridate)
library(knitr)
library(kableExtra)
library(tidyverse)
library(stringr)
library(ggplot2)
Start_Date = as.Date("1/28/2018", format = "%m/%d/%Y")
```

```{r echo = FALSE}
Update_Date = as.Date("6/23/2019", format = "%m/%d/%Y")

read_data = read.csv(file = "~/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/Running_6_23_2019.csv", skip = 1)
```

***

```{r echo = FALSE}
running = head(x = read_data, n = (Update_Date - Start_Date - 1) %>% as.integer())[, c(1, 2, 3, 4, 5, 6, 7, 11, 12, 13, 14, 18, 19, 25)]

names(running) = c("Location", "Weekday_Read", "Month_Number_Read", "Day Number", "Date", "Run Calories", "Run Distance", "Run Minutes", "Run Seconds", "Walk Calories", "Walk Distance", "Walk Minutes", "Walk Seconds", "StartTime")

running$Date         = running$Date            %>% as.Date(format = "%m/%d/%y")
running$DayNumber    = running$`Day Number`    %>% as.character() %>% as.integer()
running$RunCalories  = running$`Run Calories`  %>% as.character() %>% as.integer()
running$RunDistance  = running$`Run Distance`  %>% as.character() %>% as.numeric()
running$RunMinutes   = running$`Run Minutes`   %>% as.character() %>% as.integer()
running$RunSeconds   = running$`Run Seconds`   %>% as.character() %>% as.integer()
running$WalkCalories = running$`Walk Calories` %>% as.character() %>% as.integer()
running$WalkDistance = running$`Walk Distance` %>% as.character() %>% as.numeric()
running$WalkMinutes  = running$`Walk Minutes`  %>% as.character() %>% as.integer()
running$WalkSeconds  = running$`Walk Seconds`  %>% as.character() %>% as.integer()
running = running[ , c(1, 2, 3, 5, 14:23)]

running$Month = factor(running$Month_Number_Read)
levels(running$Month) = c(month.name, "Total")

running$Year = running$Date %>% format(format = "%Y") %>% factor(levels = c(unique(running$Date %>% format(format = "%Y"))))

running$Weekday = factor(x = running$Weekday_Read,
                         levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Total"))

running$YearMonth = paste(running$Month, " ", running$Year, sep = "") %>% factor(levels = paste(month.name, rep(running$Year %>% levels(), each = length(month.name)))[1:(Update_Date %>% format(format = "%m") %>% as.integer() %>% "+"(1) - Start_Date %>% format(format = "%m") %>% as.integer() + (Update_Date %>% format(format = "%y") %>% as.integer() - Start_Date %>% format(format = "%y") %>% as.integer()) %>% "*"(12))])

running = select(running, - Weekday_Read, - Month_Number_Read)
```

```{r echo = FALSE, eval = FALSE}
running$Treadmill = ifelse(running$Location == "Arc" | running$Location == "Ike" | running$Location == "CRCE", 1, 0)
pace_calculator = function(distance, minutes, seconds) {
  pace = (minutes * 60 + seconds) / distance
}

sum((running$Location == "Ike" | running$Location == "Arc" | running$Location == "CRCE") & running$Year == 2018)
sum((running$Location == "Ike" | running$Location == "Arc" | running$Location == "CRCE") & running$Year == 2019)
```

```{r echo = FALSE}
pace_calculator = function(distance, minutes, seconds) {
  m = ((minutes * 60 + seconds) / distance) %>% ceiling() %>% "%/%"(60)
  s = ((minutes * 60 + seconds) / distance) %>% ceiling() %>% "%%"(60)
  pace = paste(m %>% as.numeric() %>% as.character(),
               ":",
               s %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16),
               sep = "")
  return(pace)
}

yearly_mileage_pace = function(distance) {
  l = (distance / n()) %>% "*"(365) %>% "*"(100) %>% floor() %>% "/"(100)
  return(l)
}

total_time = function(minutes, seconds) {
  h = (minutes * 60 + seconds) %>% sum() %>% "%/%"(60) %>% "%/%"(60)
  m = (minutes * 60 + seconds) %>% sum() %>% "%/%"(60) %>% "%%"(60) %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  s = (minutes * 60 + seconds) %>% sum() %>% "%%"(60) %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  t = paste(h, ":", m, ":", s, sep = "")
  return(t)
}

miles_per_run = function(distance) {
  t = (distance %>% sum() / (distance > 0) %>% sum()) %>% "*"(100) %>% floor() %>% "/"(100)
  return(t)
}

miles_per_day = function(distance) {
  t = (distance %>% sum() / (n())) %>% "*"(100) %>% floor() %>% "/"(100)
  return(t)
}

miles_per_hour = function(distance, minutes, seconds) {
  t = (distance %>% sum() * 60 * 60 / (minutes * 60 + seconds)) %>% "*"(1000) %>% floor() %>% "/"(1000)
  return(t)
}
```



```{r echo = FALSE, eval = FALSE}
test = running %>%
  group_by(Year) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Pace = pace_calculator(distance = RunDistance %>% sum(),
                                   minutes = RunMinutes %>% sum(),
                                   seconds = RunSeconds %>% sum()
                                  )
            )



names(test) = c("Year", "Total Runs", "Miles", "Pace")

kable(test, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_year), bold = TRUE, font_size = 21)
```






```{r echo = FALSE, eval = FALSE}
shiny_data = write.csv(x = running,
                       file = "/Users/KevinWong/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/shiny_data.csv")

meow = read.csv(file = "/Users/KevinWong/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/shiny_data.csv")
```

```{r echo = FALSE}
total_row = c("Total",
              sum(running$RunDistance > 0),
              sum(running$RunDistance),
              "ok",
              "pace")
```

<script>
function myFunction1() {
  var x = document.getElementById("myDIV1");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}

function myFunction2() {
  var x = document.getElementById("myDIV2");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}

function myFunction3() {
  var x = document.getElementById("myDIV3");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
</script>

<style type="text/css">

td, tr {
   font-family: "Times New Roman";
   font-size: 20px;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

</style>

<h1>Kevin's Running Data</h1>

Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`

***

I enjoy running in my freetime! I have been tracking my jogging stats since January 31, 2018. Over the past `r Update_Date - Start_Date - 1` days, I have jogged `r sum(running$RunDistance)` miles across `r sum(running$RunDistance > 0)` different runs.


```{r echo = FALSE, eval = FALSE}
HM = c("Illinois Half Marathon",
          "Distance",
          "April 27, 2019",
          "1:43:29",
          "7:54",
          "364/3098",
          "275/1430",
          "36/193")
names(HM) = c("Event", "13.1 Miles", "Date", "Time", "Pace", "Rank", "Rank (Males)", "Rank (Males 20-24)")
HM = as.data.frame(HM)
kable(x = HM, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```


*** 

# Yearly Stats

```{r echo = FALSE}
groupby_year = running %>%
  group_by(Year) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            )
            )

# groupby_year = rbind(groupby_year, total_row)

names(groupby_year) = c("Year", "Total Runs", "Miles", "Time", "Pace")

groupby_year = groupby_year[order(groupby_year$Year), ]

kable(groupby_year, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_year), bold = TRUE, font_size = 21)
```

```{r echo = FALSE}
ggplot(data = groupby_year, aes(x = Year, y = Miles)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = groupby_year$Miles %>% round(digits = 2) %>% format(nsmall = 2)), vjust = 1.6, color = "white", size = 5) +
  xlab(label = "Year") +
  ylab(label = "Miles") +
  ggtitle(label = "Miles by Year") +
  theme(plot.title = element_text(hjust = 0.5))
```

<button onclick="myFunction1()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Advanced Yearly Stats </button>

<div id="myDIV1" class="collapse">  

<br />

<h3>Advanced Yearly Stats</h3>

```{r echo = FALSE}
groupby_year = running %>%
  group_by(Year) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Days_Off = sum(RunDistance == 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Miles_Per_Run = miles_per_run(
              distance = RunDistance
            ),
            
            Miles_Per_Day = miles_per_day(
              distance = RunDistance %>% sum()
            ),
            
            Yearly_Mileage_Rate = yearly_mileage_pace(
              distance = RunDistance %>% sum()
            ),

            MPH = miles_per_hour(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Calories = sum(RunCalories)
            )

names(groupby_year) = c("Year", "Total Runs", "Days Off", "Miles", "Time", "Pace", "Miles Per Run", "Miles Per Day", "Yearly Mile Rate", "MPH", "Total Calories Burned")

kable(x = groupby_year, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```

</div>


***

# Monthly Stats

```{r echo = FALSE}
groupby_yearmonth = running %>%
  group_by(YearMonth) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            )
  )

# groupby_yearmonth$yearmonth = paste(groupby_yearmonth$Month, groupby_yearmonth$Year, sep = " ")
# groupby_yearmonth = select(as.data.frame(select(groupby_yearmonth, - Month)), - Year)
# groupby_yearmonth = groupby_yearmonth[, c(ncol(groupby_yearmonth), 1:ncol(groupby_yearmonth) - 1)]
# 
# groupby_yearmonth = rbind(groupby_yearmonth, total_row)

names(groupby_yearmonth) = c("Month", "Total Runs", "Miles", "Time", "Pace")

kable(groupby_yearmonth, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) #%>%
  #row_spec(row = nrow(groupby_yearmonth), bold = TRUE, font_size = 21)
```

```{r echo = FALSE, eval = FALSE}
ggplot(data = groupby_yearmonth, aes(x = Month, y = Miles %>% as.numeric())) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = groupby_yearmonth$Miles %>% round(digits = 2) %>% format(nsmall = 2)), vjust = 1.6, color = "white", size = 2) +
  ggtitle("Month vs. Miles") +
  theme(plot.title = element_text(hjust = 0.5))
```

<button onclick="myFunction2()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Advanced Monthly Stats </button>

<div id="myDIV2" class="collapse">  

<br />

<h3>Advanced Monthly Stats</h3>

```{r echo = FALSE}
groupby_yearmonth = running %>%
  group_by(YearMonth) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Days_Off = sum(RunDistance == 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Miles_Per_Run = miles_per_run(
              distance = RunDistance
            ),
            
            Miles_Per_Day = miles_per_day(
              distance = RunDistance %>% sum()
            ),
            
            Yearly_Mileage_Rate = yearly_mileage_pace(
              distance = RunDistance %>% sum()
            ),

            MPH = miles_per_hour(
                distance = RunDistance %>% sum(),
                minutes = RunMinutes %>% sum(),
                seconds = RunSeconds %>% sum()
            ),
            
            Calories = sum(RunCalories)
            )

names(groupby_yearmonth) = c("Month", "Total Runs", "Days Off", "Miles", "Time", "Pace", "Miles Per Run", "Miles Per Day", "Yearly Mile Rate", "MPH", "Total Calories Burned")

kable(x = groupby_yearmonth, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```

</div>

***

# Weekday Stats

```{r echo = FALSE}
groupby_weekday = running %>%
  group_by(Weekday) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            )
  )
            
            # Miles_Per_Run = floor(sum(RunDistance) * 100 / sum(RunDistance > 0)) / 100,
            
            #MPH = floor(sum(RunDistance) / (((((sum(RunMinutes) + sum(RunSeconds) %/% 60) %/% 60) * 60 * 60 + ((sum(RunMinutes) + sum(RunSeconds) %/% 60) %% 60) * 60 + sum(RunSeconds) %% 60)) / (60 * 60)) * 1000) / 1000,
            
            #Calories = sum(RunCalories)
            #)

# groupby_weekday = rbind(groupby_weekday, total_row)

names(groupby_weekday) = c("Weekday", "Total Runs", "Miles", "Time", "Pace")#, "MPH", "Calories")

# names(groupby_weekday) = c("Weekday", "Total Runs", "Distance", "Time", "Pace", "Miles Per Run", "MPH", "Calories")

kable(groupby_weekday, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_weekday), bold = TRUE, font_size = 21)
```

```{r echo = FALSE}
ggplot(data = groupby_weekday, aes(x = Weekday, y = Miles)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = groupby_weekday$Miles %>% round(digits = 2) %>% format(nsmall = 2)), vjust = 1.6, color = "white", size = 5) +
  ggtitle("Weekday vs. Miles") +
  theme(plot.title = element_text(hjust = 0.5))
```

<button onclick="myFunction3()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Advanced Weekday Stats </button>

<div id="myDIV3" class="collapse">  

<br />

<h3>Advanced Weekday Stats</h3>

```{r echo = FALSE}
groupby_weekday = running %>%
  group_by(Weekday) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Days_Off = sum(RunDistance == 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Miles_Per_Run = miles_per_run(
              distance = RunDistance
            ),
            
            Miles_Per_Day = miles_per_day(
              distance = RunDistance %>% sum()
            ),
            
            Yearly_Mileage_Rate = yearly_mileage_pace(
              distance = RunDistance %>% sum()
            ),

            MPH = miles_per_hour(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Calories = sum(RunCalories)
            )

names(groupby_weekday) = c("Weekday", "Total Runs", "Days Off", "Miles", "Time", "Pace", "Miles Per Run", "Miles Per Day", "Yearly Mile Rate", "MPH", "Total Calories Burned")

kable(x = groupby_weekday, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```

</div>





```{r echo = FALSE, eval = FALSE}
location = running %>%
  group_by(Location) %>%
  summarise(Distance = sum(RunDistance),
            Time = sum(RunMinutes))

location = location[order(location$Distance, decreasing = TRUE), ] %>%
  head()
```















