---
title: "Kevin Wong - Kevin's Schoolwork"
output:
  html_document:
    toc: yes
---

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
library(kableExtra)
library(rlang)
library(tidyverse)
library(stringr)
library(ggplot2)
library(dplyr)
```

```{r echo = FALSE}
Update_Date = as.Date("05-18-2019", format = "%m-%d-%Y")
```

<style type="text/css">

.r33m_vid {
   font-family: Tahoma;
   color: white;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

.video-container {
  position: relative;
  padding-bottom: 56.25%; /* 16:9 */
  height: 0;
}
.video-container iframe {
  position: absolute;
  top: 0;
  left: 0;
  width: 100%;
  height: 100%;
}

</style>

<script>
function myFunction1() {
  var x = document.getElementById("myDIV1");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}

function myFunction2() {
  var x = document.getElementById("myDIV2");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}

function myFunction3() {
  var x = document.getElementById("myDIV3");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
</script>


***

<h1>Kevin's Schoolwork</h1>

<p class="last-updated">
Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`
</p>

***

I am a *Statistics* major at the University of Illinois. I am also minoring in *Leadership Studies* and *Business*. My GPA is 3.88.

# Courses Taken

***

## Statistics

Some of the Statistics Courses I have taken include:  

- **STAT** 385: Statistics Programming Methods            (Grade: A+)
- **STAT** 400: Statistics and Probability I              (Grade: A)
- **STAT** 410: Statistics and Probability II             (Grade: A-)
- **STAT** 420: Methods of Applied Statistics             (Grade: A)
- **STAT** 425: Applied Regression and Design             (Grade: A)
- **STAT** 432: Basics of Statistical Learning            (Grade: A)
- **STAT** 440: Statistical Data Management               (Grade: A)
- **STAT** 448: Advanced Data Analysis                    (Grade: A)

My GPA in STAT courses at U of I is 3.96.

***

## Leadership Studies

Some of the Leadership Studies Courses I have taken include:  

- **AGED** 230: Leadership Communications            (Grade: A)
- **AGED** 260: Introduction to Leadership Studies   (Grade: A+)
- **AGED** 380: Leadership in Groups and Teams       (Grade: A+)
- **AGED** 480: Collaborative Leadership             (Grade: A)

My GPA in Leadership courses at U of I is 4.00.

***

## Business

Some of the Business Courses I have taken include:  

- **BADM** 310: Management and Organizational Behavior  (Grade: A)
- **BADM** 320: Principles of Marketing                 (Grade: A+)
- **BADM** 340: Ethical Dilemmas of Business            (Grade: A+)
- **BADM** 350: IT for Networked Organizations          (Grade: A)
- **ACCY** 200: Fundamentals of Accounting              (Grade: A)
- **FIN** 221: Corporate Finance                        (Grade: A)

My GPA in Business Courses at U of I is 4.00.

***

# School Projects

<h3 class="r33m_vid">R33M Video</h3>

<div class="video-container">
<iframe src="https://www.youtube.com/embed/SG5-_hInODw" frameborder="0" allow="autoplay; encrypted-media; picture-in-picture" allowfullscreen></iframe>
</div>

***


# Psychology


<button onclick="myFunction1()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Psychology Definitions </button>

<div id="myDIV1" class="collapse">

```{r echo = FALSE}
read_data = read.csv(file = "~/Documents/KevinWebsite/kevinjameswong.github.io/files/psychology.csv", skip = 0)

read_data$Index = read_data$Kevin

psy = read_data %>% select(Index, Word, Definition)

kable(x = psy, format = "html", align = "lllll") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```


</div>
