---
title: "Kevin Wong - Kevin's Schoolwork"
output:
  html_document:
    toc: yes
---

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
library(kableExtra)
library(rlang)
library(tidyverse)
library(stringr)
library(ggplot2)
library(dplyr)
```

```{r echo = FALSE}
Update_Date = as.Date("5/18/2019", format = "%m/%d/%Y")
```

<style type="text/css">

.r33m_vid {
   font-family: Tahoma;
   color: black;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

</style>

***

<h1>Kevin's Schoolwork</h1>

Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`

***

I am a *Statistics* major at the **University of Illinois**. I am also minoring in *Leadership Studies* and *Business*. My GPA is 3.88.

# Courses Taken

***

## Statistics

Some of the Statistics Courses I have taken include:  

- **STAT** 385: Statistics Programming Methods            (Grade: A+)
- **STAT** 400: Statistics and Probability I              (Grade: A)
- **STAT** 410: Statistics and Probability II             (Grade: A-)
- **STAT** 420: Methods of Applied Statistics             (Grade: A)
- **STAT** 425: Applied Regression and Design             (Grade: A)
- **STAT** 432: Basics of Statistical Learning            (Grade: A)
- **STAT** 440: Statistical Data Management               (Grade: A)
- **STAT** 448: Advanced Data Analysis                    (Grade: A)

My GPA in STAT courses at U of I is 3.96.

***

## Leadership Studies

Some of the Leadership Studies Courses I have taken include:  

- **AGED** 230: Leadership Communications            (Grade: A)
- **AGED** 260: Introduction to Leadership Studies   (Grade: A+)
- **AGED** 380: Leadership in Groups and Teams       (Grade: A+)
- **AGED** 480: Collaborative Leadership             (Grade: A)

My GPA in Leadership courses at U of I is 4.00.

***

## Business

Some of the Business Courses I have taken include:  

- **BADM** 310: Management and Organizational Behavior  (Grade: A)
- **BADM** 320: Principles of Marketing                 (Grade: A+)
- **BADM** 340: Ethical Dilemmas of Business            (Grade: A+)
- **BADM** 350: IT for Networked Organizations          (Grade: A)
- **ACCY** 200: Fundamentals of Accounting              (Grade: A)
- **FIN** 221: Corporate Finance                        (Grade: A)

My GPA in Business Courses at U of I is 4.00.

***

# School Projects

<h3 class="r33m_vid">R33M Video</h3>

<iframe width="672" height="378" src="https://www.youtube.com/embed/SG5-_hInODw" frameborder="0" allow="autoplay; encrypted-media; picture-in-picture" allowfullscreen></iframe>



