---
title: "Kevin Wong - Sleeping Data"
output:
  html_document:
    toc: yes
---
<!--
<style>
body .main-container {
  max-width: 900px !important;
}
</style>

-->
<!--
<style>
body .main-container {
  background-color: #FF8200 !important;
  max-width: 900px !important;
}
</style>
-->

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(lubridate)
library(knitr)
library(kableExtra)
library(tidyverse)
library(stringr)
library(ggplot2)
library(dplyr)

Start_Date = as.Date("02-07-2017", format = "%m-%d-%Y")

percent = function(x, digits = 2, format = "f", ...) {
  formatC(x, format = format, digits = digits, ...) %>% paste("%", sep = "")
}
```

```{r echo = FALSE}
round_down_2_decimals = function(x, digits = 2, format = "f", ...) {
  x %>% "*"(100) %>% floor() %>% "/"(100) %>% formatC(format = "f", digits = 2)
}
```

```{r echo = FALSE}
Update_Date = as.Date("06-28-2019", format = "%m-%d-%Y")

# The morning of the last sleep

sleep = read.csv("~/Documents/KevinWebsite/kevinjameswong.github.io/files/sleepdata_6_28_2019.csv", sep = ";")
```

```{r echo = FALSE}
total_time = function(seconds) {
  h = seconds %>% sum() %>% "%/%"(60) %>% "%/%"(60)
  m = seconds %>% sum() %>% "%/%"(60) %>% "%%"(60) %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  s = seconds %>% sum() %>% "%%"(60) %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  t = paste(h, ":", m, ":", s, sep = "")
  return(t)
}

minutes_to_time = function(insert_min) {
  hours = insert_min %>% sum() %>% "%/%"(60) %>% floor()
  minutes = insert_min %>% sum() %>% "%%"(60) %>% floor() %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  return(paste(hours, ":", minutes, sep = ""))
}
```

```{r echo = FALSE}
sleep$Sleep.quality = str_extract(string = sleep$Sleep.quality, pattern = "[0-9]{1,3}") %>% as.integer()
sleep$Time.in.bed = str_extract(string = sleep$Time.in.bed, pattern = "[0-9]{1,2}") %>% as.integer() * (60) + (str_extract(string = sleep$Time.in.bed, pattern = ":[0-9]{1,2}") %>% str_extract(pattern = "[0-9]{1,2}") %>% as.integer()) %>% as.integer()


sleep$enddates = str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date()

add_on = cbind(matrix(setdiff(c(as.Date(1:(Update_Date - Start_Date), origin = Start_Date)), str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date()),
                      nrow = length(setdiff(c(as.Date(1:(Update_Date - Start_Date), origin = Start_Date)), str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date())),
                      ncol = 1),
              matrix(NA,
                     nrow = length(setdiff(c(as.Date(1:(Update_Date - Start_Date), origin = Start_Date)), str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date())),
                     ncol = ncol(sleep) - 1)) %>% as.data.frame()
add_on$V1 = as.Date(add_on$V1, origin = "1970-01-01", tz = "CDT")
names(add_on) = names(sleep)
add_on$enddates = add_on$Start
add_on$Start = add_on$End

sleep = rbind(sleep, add_on)

sleep = sleep[order(sleep$enddates, decreasing = FALSE), ]

sleep$Weekday = factor(x = rep(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"), len = nrow(sleep)),
                       levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Total", "Average"))

sleep$theo_startdates = sleep$enddates - 1

sleep$Year = sleep$theo_startdates %>%
  format(format = "%Y") %>%
  factor(levels = sleep$theo_startdates %>%
           format(format = "%Y") %>%
           unique() %>%
           sort()
         )

sleep$Month = sleep$theo_startdates %>%
  format(format = "%m") %>%
  factor(levels = sleep$theo_startdates %>%
           format(format = "%m") %>%
           unique() %>%
           sort()
         )

sleep$YearMonth = paste(sleep$Month, " ", sleep$Year, sep = "") %>% factor(levels = paste(month.name, rep(sleep$Year %>% levels(), each = length(month.name)))[1:(Update_Date %>% format(format = "%m") %>% as.integer() %>% "+"(1) - Start_Date %>% format(format = "%m") %>% as.integer() + (Update_Date %>% format(format = "%y") %>% as.integer() - Start_Date %>% format(format = "%y") %>% as.integer()) %>% "*"(12))])

sleep$Start = sleep$Start %>% as.POSIXct(format = "%Y-%m-%d %H:%M:%S")
sleep$End = sleep$End %>% as.POSIXct(format = "%Y-%m-%d %H:%M:%S")

sleep$duration = difftime(time1 = sleep$End, time2 = sleep$Start, units = "sec") #%>% "/"(60)

sleep$sa3_sleep_start = difftime(time1 = sleep$Start, time2 = str_extract(string = sleep$theo_startdates, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% paste(" 18:00:00 PM", sep = "") %>% as.POSIXct(format = "%Y-%m-%d %H:%M:%S"), units = "sec")
sleep$sb3_sleep_end = difftime(time1 = str_extract(string = sleep$enddates, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% paste(" 18:00:00 PM", sep = "") %>% as.POSIXct(format = "%Y-%m-%d %H:%M:%S"), time2 = sleep$End, units = "sec")
```

```{r echo = FALSE}
to_bed_time = function(s) {
  k = (today() %>% paste(" 18:00:00 PM", sep = "") %>% as.POSIXct(format = "%Y-%m-%d %H:%M:%S %p") + s) %>% strftime(format = "%r")
  return(k)
}

wake_ups_time = function(s) {
  k = (today() %>% paste(" 18:00:00 PM", sep = "") %>% as.POSIXct(format = "%Y-%m-%d %H:%M:%S %p") - s) %>% strftime(format = "%r")
  return(k)
}
```

```{r echo = FALSE}
seconds_to_time = function(insert_seconds) {

a = ifelse(test = insert_seconds %/% (60 * 60) == 0,
       yes = 0,
       no = insert_seconds %/% (60 * 60) %>% strptime(format = "%S") %>% str_extract(pattern = ":[0-9]{2}:[0-9]{1,2}") %>% str_extract(pattern = "[0-9]{1}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.integer())

a = ifelse(a >= 13,
           yes = paste(a - 12, sep = ""),
           no = ifelse(a == 12,
                       yes = "12",
                       no = paste(a, sep = "")))

b = ifelse(test = insert_seconds %/% 60 %% 60 == 0,
       yes = "00" %>% paste(sep = ""),
       no = insert_seconds %/% 60 %% 60 %>% strptime(format = "%S") %>% str_extract(pattern = ":[0-9]{2}:[0-9]{1,2}") %>% str_extract(pattern = "[0-9]{1}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.character())

c = ifelse(test = insert_seconds %% 60 == 0,
       yes = "00" %>% paste(sep = ""),
       no = insert_seconds %% 60 %>% strptime(format = "%S") %>% str_extract(pattern = ":[0-9]{2}:[0-9]{1,2}") %>% str_extract(pattern = "[0-9]{1}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.character())

d = ifelse(test = a >= 6 & a <= 11,
           yes = "PM",
           no = "AM")



meow = strptime(paste(a, b, c, sep = ":"), format = "%H:%M:%S")
e = str_extract(string = meow, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}")
f = paste(e, " ", d, sep = "")
return(f)
}
```

<h1>Kevin's Sleeping Data</h1>

<p class="last-updated">
Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`
</p>

***

<style type="text/css">

td, tr {
   font-family: "Times New Roman";
   font-size: 20px;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

</style>

I have been tracking my sleeping stats since February 6, 2017 using the [Sleep Cycle](https://www.sleepcycle.com){target="_blank"} app. Over the past `r nrow(sleep)` days, here are statistics on my past `r nrow(sleep) - (is.na(sleep$Sleep.quality) %>% sum())` sleeps.

***

# Yearly Stats

```{r echo = FALSE}
options(dplyr.summarise.inform = FALSE)

groupby_year = sleep %>%
  group_by(Year) %>%
  summarise(total = Sleep.quality %>% ">="(0) %>% sum(na.rm = TRUE),
            avg_quality = Sleep.quality %>% mean(na.rm = TRUE) %>% round_down_2_decimals(),
            time_in_bed = mean(Time.in.bed, na.rm = TRUE) %>% minutes_to_time(),
            to_bed = sa3_sleep_start %>% mean(na.rm = TRUE) %>% to_bed_time(),
            wake_ups_time_litty = sb3_sleep_end %>% mean(na.rm = TRUE) %>% wake_ups_time()
           # nap_prob = paste((Sleep.Notes %>% str_detect(pattern = "Took a nap \\(1 hour\\)") %>% sum(na.rm = TRUE) + Sleep.Notes %>% str_detect(pattern = "Took a nap \\(1.5 hours\\)") %>% sum(na.rm = TRUE) + Sleep.Notes %>% str_detect(pattern = "Took a nap \\(2 hours\\)") %>% sum(na.rm = TRUE)) %>% "/"(Sleep.quality %>% ">="(0) %>% sum(na.rm = TRUE)) %>% "*"(10000) %>% floor() %>% "/"(100), "%", sep = "")
            #avg_footsteps = Activity..steps. %>% mean(na.rm = TRUE) %>% floor()
            )
```

```{r echo = FALSE, warning = FALSE}
names(groupby_year) = c("Year", "Total Nights", "Sleep Quality (%)", "Average Time in Bed", "Asleep Time", "Wake Up Time")

kable(groupby_year, format = "html", align = "lrrcrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))
```

```{r echo = FALSE, warning = FALSE}
ggplot(data = groupby_year, aes(x = Year, y = `Sleep Quality (%)` %>% as.numeric())) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = percent(`Sleep Quality (%)`)), vjust = 1.6, color = "white", size = 5) +
  ggtitle(label = "Sleep Quality vs. Year") +
  xlab(label = "Year") +
  ylab(label = "Sleep Quality") +
  coord_cartesian(ylim = c(85, 90.25)) + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.text.x = element_text(size = 13, color = "black"),
        axis.text.y = element_text(size = 13, color = "black"),
        axis.title.x = element_text(size = 14, color = "black"),
        axis.title.y = element_text(size = 14, color = "black"))
```

***

# Weekday Stats

```{r echo = FALSE, warning = FALSE}
# options(dplyr.summarise.inform = FALSE)

groupby_weekday = sleep %>%
  group_by(Weekday) %>%
  summarise(total = Sleep.quality %>% ">="(0) %>% sum(na.rm = TRUE),
            avg_quality = Sleep.quality %>% mean(na.rm = TRUE) %>% round_down_2_decimals(),
            time_in_bed = mean(Time.in.bed, na.rm = TRUE) %>% minutes_to_time(),
            to_bed = sa3_sleep_start %>% mean(na.rm = TRUE) %>% to_bed_time(),
            wake_ups_time_litty = sb3_sleep_end %>% mean(na.rm = TRUE) %>% wake_ups_time()
            #bed_time = (ifelse(test = str_extract(string = Start, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) %>% "*"(60) <= 60 * 60 * 12, yes = str_extract(string = Start, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) %>% "*"(60) %>% "+"(60 * 60 *24), no = str_extract(string = Start, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) %>% "*"(60)) + str_extract(string = Start, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = ":[0-9]{2}:") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) + str_extract(string = Start, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = ":[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{1}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() - (60 * 60 * 12)) %>% as.numeric() %>% mean(na.rm = TRUE) %>% seconds_to_time(),
            #wake_time = (ifelse(test = str_extract(string = End, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) %>% "*"(60) <= 60 * 60 * 12, yes = str_extract(string = End, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) %>% "*"(60) %>% "+"(60 * 60 *24), no = str_extract(string = End, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) %>% "*"(60)) + str_extract(string = End, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = ":[0-9]{2}:") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() %>% "*"(60) + str_extract(string = End, pattern = "[0-9]{2}:[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = ":[0-9]{2}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{1}:[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric() - (60 * 60 * 12)) %>% as.numeric() %>% mean(na.rm = TRUE) %>% seconds_to_time()
           # nap_prob = paste((Sleep.Notes %>% str_detect(pattern = "Took a nap \\(1 hour\\)") %>% sum(na.rm = TRUE) + Sleep.Notes %>% str_detect(pattern = "Took a nap \\(1.5 hours\\)") %>% sum(na.rm = TRUE) + Sleep.Notes %>% str_detect(pattern = "Took a nap \\(2 hours\\)") %>% sum(na.rm = TRUE)) %>% "/"(Sleep.quality %>% ">="(0) %>% sum(na.rm = TRUE)) %>% "*"(10000) %>% floor() %>% "/"(100), "%", sep = "")
            #avg_footsteps = Activity..steps. %>% mean(na.rm = TRUE) %>% floor()
            )
```

```{r echo = FALSE, eval = FALSE}
total_count = sum(sleep$Sleep.quality >= 0, na.rm = TRUE)
total_avg_sleep = mean(sleep$Sleep.quality, na.rm = TRUE) %>% round_down_2_decimals()
total_avg_bed = sleep$Time.in.bed %>% mean(na.rm = TRUE) %>% minutes_to_time()

total_row = c("Total", total_count, total_avg_sleep, total_avg_bed)#, 1, 2)

groupby_weekday = rbind(groupby_weekday, total_row)
```

```{r echo = FALSE}
names(groupby_weekday) = c("Day", "Total Nights", "Sleep Quality (%)", "Average Time in Bed", "Avg Asleep Time", "Avg Wake Up Time")

kable(groupby_weekday, format = "html", align = "lcccccc") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_weekday), bold = TRUE, font_size = 21)
```

```{r echo = FALSE, eval = FALSE}
groupby_weekday = groupby_weekday[1:(nrow(groupby_weekday) - 1), ]

avg_row = c("Average", total_count, total_avg_sleep, total_avg_bed)

groupby_weekday = rbind(groupby_weekday, avg_row)
```

```{r echo = FALSE}

options(dplyr.summarise.inform = FALSE)

ggplot(data = groupby_weekday, aes(x = Day, y = `Sleep Quality (%)` %>% as.numeric())) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = percent(`Sleep Quality (%)`)), vjust = 1.6, color = "white", size = 4) +
  ggtitle(label = "Sleep Quality vs. Weekday") +
  xlab(label = "Weekday") +
  ylab(label = "Sleep Quality") +
  coord_cartesian(ylim = c(85, 90.25)) + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        axis.text.x = element_text(size = 12, color = "black"),
        axis.text.y = element_text(size = 12, color = "black"),
        axis.title.x = element_text(size = 14, color = "black"),
        axis.title.y = element_text(size = 14, color = "black"))
```


<a href="#top">Back to top</a>


```{r echo = FALSE, eval = FALSE}
If you want to create a drop down element, you have to look into `html forms` and `select option`.
```


