---
title: "Kevin Wong - Sleeping Data"
output:
  html_document:
    toc: yes
---

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
library(stringr)
Start_Date = as.Date("2/7/2017", format = "%m/%d/%Y")

Update_Months = c("January", "February", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December")

percent = function(x, digits = 2, format = "f", ...) {
  formatC(100 * x, format = format, digits = digits, ...) %>% paste("%", sep = "")
}
```

```{r echo = FALSE}
round_down_2_decimals = function(x, digits = 2, format = "f", ...) {
  x %>% "*"(100) %>% floor() %>% "/"(100) %>% formatC(format = "f", digits = 2)
}
```

```{r echo = FALSE}
Update_Date = as.Date("4/8/2019", format = "%m/%d/%Y")

# The morning of the last sleep
```

```{r echo = FALSE}
sleep = read.csv("~/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/sleepdata.csv", sep = ";")
```

```{r echo = FALSE}
minutes_to_time = function(insert_min) {
  hours = insert_min %/% 60 %>% as.character()
  minutes = strptime(insert_min %% 60, format="%M") %>% str_extract(pattern = ":[0-9]{1,2}:") %>% str_extract(pattern = "[0-9]{1,2}")
  return(paste(hours, ":", minutes, sep = ""))
}
```

```{r echo = FALSE}
sleep$Sleep.quality = str_extract(string = sleep$Sleep.quality, pattern = "[0-9]{1,3}") %>% as.integer()
sleep$Time.in.bed = str_extract(string = sleep$Time.in.bed, pattern = "[0-9]{1,2}") %>% as.integer() * (60) + (str_extract(string = sleep$Time.in.bed, pattern = ":[0-9]{1,2}") %>% str_extract(pattern = "[0-9]{1,2}") %>% as.integer()) %>% as.integer()


sleep$enddates = str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date()

add_on = cbind(matrix(setdiff(c(as.Date(1:(Update_Date - Start_Date), origin = Start_Date)), str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date()),
                      nrow = length(setdiff(c(as.Date(1:(Update_Date - Start_Date), origin = Start_Date)), str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date())),
                      ncol = 1),
              matrix(NA,
                     nrow = length(setdiff(c(as.Date(1:(Update_Date - Start_Date), origin = Start_Date)), str_extract(string = sleep$End, pattern = "[0-9]{4}-[0-9]{2}-[0-9]{2}") %>% as.Date())),
                     ncol = ncol(sleep) - 1)) %>% as.data.frame()
add_on$V1 = as.Date(add_on$V1, origin = "1970-01-01")
names(add_on) = names(sleep)
add_on$enddates = add_on$Start
add_on$Start = add_on$End

sleep = rbind(sleep, add_on)

sleep = sleep[order(sleep$enddates, decreasing = FALSE), ]

sleep$Weekday = factor(x = rep(c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"), len = nrow(sleep)),
                       levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Total"))
```

<h1>Kevin's Sleeping Data</h1>

Last updated: `r paste(Update_Months[str_extract(string = Update_Date, pattern = "-[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric()], " ", str_extract(string = Update_Date, pattern = "-[0-9]{2}-[0-9]{2}") %>% str_extract(pattern = "[0-9]{1}-[0-9]{2}") %>% str_extract(pattern = "[0-9]{2}") %>% as.numeric(), ", ", str_extract(string = Update_Date, pattern = "[0-9]{4}") %>% as.numeric(), sep = "")`

***

<style type="text/css">

td, tr {
   font-family: "Times New Roman";
   font-size: 20px;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

</style>

I have been tracking my sleeping stats since February 6, 2017 using the [Sleep Cycle](https://www.sleepcycle.com){target="_blank"} app. It's a phenomenal app. Over the past `r nrow(sleep)` days, here are statistics on my past `r nrow(sleep) - (is.na(sleep$Sleep.quality) %>% sum())` sleeps.

***

```{r echo = FALSE}
groupby_weekday = sleep %>%
  group_by(Weekday) %>%
  summarise(total = Sleep.quality %>% ">="(0) %>% sum(na.rm = TRUE),
            avg_quality = Sleep.quality %>% mean(na.rm = TRUE) %>% round_down_2_decimals(),
            time_in_bed = mean(Time.in.bed, na.rm = TRUE) %>% minutes_to_time()
           # nap_prob = paste((Sleep.Notes %>% str_detect(pattern = "Took a nap \\(1 hour\\)") %>% sum(na.rm = TRUE) + Sleep.Notes %>% str_detect(pattern = "Took a nap \\(1.5 hours\\)") %>% sum(na.rm = TRUE) + Sleep.Notes %>% str_detect(pattern = "Took a nap \\(2 hours\\)") %>% sum(na.rm = TRUE)) %>% "/"(Sleep.quality %>% ">="(0) %>% sum(na.rm = TRUE)) %>% "*"(10000) %>% floor() %>% "/"(100), "%", sep = "")
            #avg_footsteps = Activity..steps. %>% mean(na.rm = TRUE) %>% floor()
            )
```


```{r echo = FALSE}
total_count = sum(sleep$Sleep.quality >= 0, na.rm = TRUE)
total_avg_sleep = mean(sleep$Sleep.quality, na.rm = TRUE) %>% round_down_2_decimals()
```

```{r echo = FALSE}
total_avg_bed = sleep$Time.in.bed %>% mean(na.rm = TRUE) %>% minutes_to_time()
```

```{r echo = FALSE, warning = FALSE}
total_row = c("Total", total_count, total_avg_sleep, total_avg_bed)
```

```{r echo = FALSE}
groupby_weekday = rbind(groupby_weekday, total_row)
```




```{r echo = FALSE}
names(groupby_weekday) = c("Weekday", "Sleeps Recorded", "Sleep Quality (%)", "Average Time in Bed")#"Yeet")#, "Average Footsteps")

kable(groupby_weekday, format = "html", align = "lrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  row_spec(nrow(groupby_weekday), bold = TRUE)
```


