---
title: "Kevin Wong - Music Data"
output:
  html_document:
    toc: yes
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
Update_Date = as.Date("01-01-2025", format = "%m-%d-%Y")
#Update_Date

library(dplyr)
library(gghighlight)
library(ggplot2)
library(kableExtra)
library(knitr)
library(lubridate)
library(rlang)
library(shiny)
library(shinydashboard)
library(stringr)
library(tidyverse)
```

<style type="text/css">
body .main-container {
	max-width: 1080px !important;
}
</style>

<h1>Spotify Wrapped Data</h1>

<p class="last-updated">
Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`
</p>

<hr />

```{r}
ggplot(data = spotify %>% filter(Year == 2016), aes(AlbumYear, y = n())) 
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
spotify = read.csv(file = "files/SpotifyWrapped.csv")

spotify =
  spotify %>%
  select(
    Year,
    Ranking,
    Song,
    Album,
    Artist1,
    Artist2,
    Artist3,
    Artist4,
    Artist5,
    Artist6,
    SongID,
    AlbumID,
    Artist1ID,
    Artist2ID,
    Artist3ID,
    Artist4ID,
    Artist5ID,
    Artist6ID,
    ApproxGenre,
    Album.Year,
    Song.Length
  )

spotify = spotify %>%
  group_by(Year) %>%
  mutate(
    Score = max(row_number()) + 1 - row_number(),
    Count = 1,
    RecordInt = row_number()
  ) %>%
  filter(Song != "")

names(spotify) = c("Year", "SongRanking", "Song", "Album", "ArtistName", "Artist2Name", "Artist3Name", "Artist4Name", "Artist5Name", "Artist6Name", "SongID", "AlbumID", "Artist1ID", "Artist2ID", "Artist3ID", "Artist4ID", "Artist5ID", "Artist6ID", "Genre", "AlbumYear", "SongLengthChar", "Score", "Count", "RecordInt")

spotify$TotalSeconds = (str_sub(string = spotify$SongLengthChar, start = 1, end = 1) %>% as.integer() * 60) + str_sub(string = spotify$SongLengthChar, start = 3) %>% as.integer()
spotify$Minutes = spotify$TotalSeconds %>% ceiling() %>% "%/%"(60)
spotify$Seconds = spotify$TotalSeconds %>% ceiling() %>% "%%"(60)
```

```{r}
spotify$YearDifference = spotify$Year - spotify$AlbumYear
```

```{r}
lasf = c(2, 3)
lasf %>% mean() + 2
```


<p class="last-updated">
I have been collecting my Spotify Wrapped data since `r min(spotify$Year)`. I have `r length(table(spotify$Year))` years worth of data, from `r min(spotify$Year)` - `r max(spotify$Year)`.
</p>

<div class="shiny-container">
<iframe src="https://kevinjameswong.shinyapps.io/spotify/">
</iframe>
</div>


