---
title: "Kevin Wong - Running Data"
output:
  html_document:
    toc: yes
---

```{r echo = FALSE, eval = FALSE}
Add 12 month difference green if higher red if lower
Add Year to Year difference

Add miles needed to beat last year/last month

Add run intensity.

Fuseball example. Rankings system. Win Loss ranking. ID number for each person. If Kevin who is 3-0 beats Bob who is 1-2, computer projects score to be Kevin 10 - Bob 3.7. If Kevin wins, his win/loss ranking goes up. Bobs goes down. However, if Kevin wins 10-8, Kevin''s win/loss ranking goes up but his ELO scoring goes down.

Making new table into aggregate table like Compass Mortgage grouped by day. Continue to use miles per hour formula to calculate pace. But need to use group by a little bit more.
```


```{r echo = FALSE, warning = FALSE, message = FALSE}
library(lubridate)
library(knitr)
library(kableExtra)
library(tidyverse)
library(stringr)
library(ggplot2)
```

```{r echo = FALSE}
read_data = read.csv(file = "~/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/Running_10_12_2019.csv", skip = 1)

start_date = read_data$Date[read_data$Run.Distance %>% is.na() %>% `!` %>% which() %>% min()]
update_date = read_data$Date[read_data$Run.Distance %>% is.na() %>% `!` %>% which() %>% max()]
```

***

```{r}
View(read_data)

read_data %>%
  group_by(Date %>% as.Date(format = "%m/%d/%y")) %>%
  summarize(Yeet = sum(Run.Calories),
            RunDistance = sum(Run.Distance),
            RunSeconds = sum(Run.Seconds) + sum(Run.Minutes) * 60,
            NumberOfRuns = sum(Run.Distance > 0)) %>%
  filter(is.na(Run.Distance) == FALSE) %>%
  View()

read_data %>%
  mutate(Run.Calories / Run.Minutes) %>%
  View()

read_data$Date %>% as.Date(format = "%m/%d/%y") %>% max(na.rm = TRUE)
read_date$Dat
read_data$Date %>% as.Date(format = "%m/%d/%y") %>% filter(!is.na(Run.Distance)) %>% View()
```


```{r}
read_data$Date = read_data$Date %>% as.Date(format = "%m/%d/%y")
View(read_data)

read_data[621, 5]

sessionInfo()


which.max(read_data$Date)

read_data$Run.Calories %>% is.na() %>% max()
```



```{r}
tail(read_data$Run.Distance[read_data$Run.Distance != NA])

max(which(!is.na(read_data$Run.Distance)))


update_date = read_data$Date[read_data$Run.Distance %>% is.na() %>% `!` %>% which() %>% max()]
```

```{r}
read_data = read_data %>%
  filter(is.na(Run.Distance) == FALSE) %>%
  mutate(Date = Date %>% as.Date(format = "%m/%d/%y")) %>%
  select(Location,
         Day,
         Month,
         Day.1,
         Date,
         Run.Calories,
         Run.Distance,
         Run.Minutes,
         Run.Seconds,
         Walk.Calories,
         Walk.Distance,
         Walk.Minutes,
         Walk.Seconds,
         Start.Time,
         Notes)

unique_dates = (read_data$Date %>% min()):
          (read_data$Date %>% max()) %>% as.Date(origin = "1970-01-01") %>% as.data.frame()
names(unique_dates) = c("HELLO")

View(unique_dates)
```


```{r}
test = read_data %>%
  group_by(t = Date %>% as.Date(format = "%m/%d/%y")) %>%
  summarize(RunCalories = sum(Run.Calories),
            RunDistance = sum(Run.Distance),
            RunSeconds = sum(Run.Seconds) + sum(Run.Minutes) * 60,
            WalkCalories = sum(Walk.Calories),
            WalkDistance = sum(Walk.Distance),
            WalkSeconds = sum(Walk.Seconds) + sum(Run.Minutes) * 60,
            NumberOfRuns = sum(Run.Distance > 0),
            Ike = sum(Location == "Ike"),
            Outside = sum(Location == "Outside"),
            CRCE = sum(Location == "CRCE")
            ) %>%
  filter(is.na(RunDistance) == FALSE)

View(start)
```


```{r}
t %>% left_join(test, by = "t")
```



```{r}
read_data %>%
  filter(is.na(Run.Calories) == FALSE) %>%
  group_by(Date %>% as.Date(format = "%m/%d/%y")) %>%
  summarize(dailyCalories = sum(Run.Calories),
            dailyDistance = sum(Run.Distance),
            dailySeconds = sum(Run.Seconds) + sum(Run.Minutes) * 60,
            dailyRuns = sum(Run.Distance > 0),
            dailyOff = sum(Run.Distance == 0, Run.Minutes == 0) / 2) %>%
  View()
```




```{r echo = FALSE}
running = read_data %>%
  select(Location,
         Day,
         Month,
         Day.1,
         Date,
         Run.Calories,
         Run.Distance,
         Run.Minutes,
         Run.Seconds,
         Walk.Calories,
         Walk.Distance,
         Walk.Minutes,
         Walk.Seconds,
         Start.Time) %>%
  slice(1:(Update_Date - Start_Date - 1) %>% as.integer())

names(running) = c("Location", "Weekday_Read", "Month_Number_Read", "Day Number", "Date", "Run Calories", "Run Distance", "Run Minutes", "Run Seconds", "Walk Calories", "Walk Distance", "Walk Minutes", "Walk Seconds", "StartTime")

running$Date         = running$Date            %>% as.Date(format = "%m/%d/%y")
running$DayNumber    = running$`Day Number`    %>% as.character() %>% as.integer()
running$RunCalories  = running$`Run Calories`  %>% as.character() %>% as.integer()
running$RunDistance  = running$`Run Distance`  %>% as.character() %>% as.numeric()
running$RunMinutes   = running$`Run Minutes`   %>% as.character() %>% as.integer()
running$RunSeconds   = running$`Run Seconds`   %>% as.character() %>% as.integer()
running$WalkCalories = running$`Walk Calories` %>% as.character() %>% as.integer()
running$WalkDistance = running$`Walk Distance` %>% as.character() %>% as.numeric()
running$WalkMinutes  = running$`Walk Minutes`  %>% as.character() %>% as.integer()
running$WalkSeconds  = running$`Walk Seconds`  %>% as.character() %>% as.integer()

running = running %>%
  select(Location,
         Weekday_Read,
         Month_Number_Read,
         Date,
         StartTime,
         DayNumber,
         RunCalories,
         RunDistance,
         RunMinutes,
         RunSeconds,
         WalkCalories,
         WalkDistance,
         WalkMinutes,
         WalkSeconds)

running$Month = factor(running$Month_Number_Read)
levels(running$Month) = c(month.name, "Total")

running$Year = running$Date %>%
  format(format = "%Y") %>%
  factor(levels = running$Date %>%
           format(format = "%Y") %>%
           unique() %>%
           sort()
         )

running$Weekday = factor(x = running$Weekday_Read,
                         levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Total"))

running$YearMonth = paste(running$Month, " ", running$Year, sep = "") %>% factor(levels = paste(month.name, rep(running$Year %>% levels(), each = length(month.name)))[1:(Update_Date %>% format(format = "%m") %>% as.integer() %>% "+"(1) - Start_Date %>% format(format = "%m") %>% as.integer() + (Update_Date %>% format(format = "%y") %>% as.integer() - Start_Date %>% format(format = "%y") %>% as.integer()) %>% "*"(12))])

running = select(running, - Weekday_Read, - Month_Number_Read)

running$Treadmill = ifelse(running$Location == "Arc" | running$Location == "Ike" | running$Location == "CRCE", 1, 0)

running$CumRunDistance = cumsum(running$RunDistance)
```




```{r echo = FALSE, eval = FALSE}
eTs
running$streak = ave(eTs, cumsum(eTs == 0), FUN = seq_along) - 1

t = data.frame(
  Date = running$Date,
  RunDistance = running$RunDistance,
  streak = running$streak
)
V
```

```{r echo = FALSE}
pace_calculator = function(distance, minutes, seconds) {
  m = ((minutes * 60 + seconds) / distance) %>% ceiling() %>% "%/%"(60)
  s = ((minutes * 60 + seconds) / distance) %>% ceiling() %>% "%%"(60)
  pace = paste(m %>% as.numeric() %>% as.character(),
               ":",
               s %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16),
               sep = "")
  return(pace)
}

yearly_mileage_pace = function(distance) {
  l = (distance / n()) %>% "*"(365) %>% "*"(100) %>% floor() %>% "/"(100)
  return(l)
}

total_time = function(minutes, seconds) {
  h = (minutes * 60 + seconds) %>% sum() %>% "%/%"(60) %>% "%/%"(60)
  m = (minutes * 60 + seconds) %>% sum() %>% "%/%"(60) %>% "%%"(60) %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  s = (minutes * 60 + seconds) %>% sum() %>% "%%"(60) %>% paste(":01 ", today(), sep = "") %>% as.POSIXct(format = "%M:%S %Y-%m-%d") %>% str_sub(start = 15, end = 16)
  t = paste(h, ":", m, ":", s, sep = "")
  return(t)
}

miles_per_run = function(distance) {
  t = (distance %>% sum() / (distance > 0) %>% sum()) %>% "*"(100) %>% floor() %>% "/"(100)
  return(t)
}

miles_per_day = function(distance) {
  t = (distance %>% sum() / (n())) %>% "*"(100) %>% floor() %>% "/"(100)
  return(t)
}

miles_per_hour = function(distance, minutes, seconds) {
  t = (distance %>% sum() * 60 * 60 / (minutes * 60 + seconds)) %>% "*"(1000) %>% floor() %>% "/"(1000)
  return(t)
}
```


```{r}
miles_per_hour(
  distance = 62.43,
  minutes = 0,
  seconds = 30780
)

```

```{r echo = FALSE, eval = FALSE}
test = running %>%
  group_by(Year) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Pace = pace_calculator(distance = RunDistance %>% sum(),
                                   minutes = RunMinutes %>% sum(),
                                   seconds = RunSeconds %>% sum()
                                  )
            )



names(test) = c("Year", "Total Runs", "Miles", "Pace")

kable(test, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_year), bold = TRUE, font_size = 21)
```






```{r echo = FALSE, eval = FALSE}
shiny_data = write.csv(x = running,
                       file = "/Users/KevinWong/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/shiny_data.csv")

meow = read.csv(file = "/Users/KevinWong/Documents/Kevin Stuff/Not Work/website/Website Files/more website files/shiny_data.csv")
```

```{r echo = FALSE}
total_row = c("Total",
              sum(running$RunDistance > 0),
              sum(running$RunDistance),
              "ok",
              "pace")
```

<script>
function myFunction1() {
  var x = document.getElementById("myDIV1");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}

function myFunction2() {
  var x = document.getElementById("myDIV2");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}

function myFunction3() {
  var x = document.getElementById("myDIV3");
  if (x.style.display === "block") {
    x.style.display = "none";
  } else {
    x.style.display = "block";
  }
}
</script>

<style type="text/css">

td, tr {
   font-family: "Times New Roman";
   font-size: 20px;
}

body, p {
   font-family: "Times New Roman";
   font-size: 18px;
}

</style>

<h1>Kevin's Running Data</h1>

Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`

***

I enjoy running in my freetime! I have been tracking my jogging stats since January 31, 2018. Over the past `r Update_Date - Start_Date - 1` days, I have jogged `r sum(running$RunDistance)` miles across `r sum(running$RunDistance > 0)` different runs.


```{r echo = FALSE, eval = FALSE}
HM = c("Illinois Half Marathon",
          "Distance",
          "April 27, 2019",
          "1:43:29",
          "7:54",
          "364/3098",
          "275/1430",
          "36/193")
names(HM) = c("Event", "13.1 Miles", "Date", "Time", "Pace", "Rank", "Rank (Males)", "Rank (Males 20-24)")
HM = as.data.frame(HM)
kable(x = HM, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```


*** 

# Yearly Stats

```{r echo = FALSE}
groupby_year = running %>%
  group_by(Year) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            )
            )

# groupby_year = rbind(groupby_year, total_row)

names(groupby_year) = c("Year", "Total Runs", "Miles", "Time", "Pace")

groupby_year = groupby_year[order(groupby_year$Year), ]

kable(groupby_year, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_year), bold = TRUE, font_size = 21)
```

```{r echo = FALSE}
ggplot(data = groupby_year, aes(x = Year, y = Miles)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = groupby_year$Miles %>% round(digits = 2) %>% format(nsmall = 2)), vjust = 1.6, color = "white", size = 5) +
  xlab(label = "Year") +
  ylab(label = "Miles") +
  ggtitle(label = "Miles by Year") +
  theme(plot.title = element_text(hjust = 0.5))
```

<button onclick="myFunction1()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Advanced Yearly Stats </button>

<div id="myDIV1" class="collapse">  

<br />

<h3>Advanced Yearly Stats</h3>

```{r echo = FALSE}
groupby_year = running %>%
  group_by(Year) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Days_Off = sum(RunDistance == 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Miles_Per_Run = miles_per_run(
              distance = RunDistance
            ),
            
            Miles_Per_Day = miles_per_day(
              distance = RunDistance %>% sum()
            ),
            
            Yearly_Mileage_Rate = yearly_mileage_pace(
              distance = RunDistance %>% sum()
            ),

            MPH = miles_per_hour(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Calories = sum(RunCalories)
            )

names(groupby_year) = c("Year", "Total Runs", "Days Off", "Miles", "Time", "Pace", "Miles Per Run", "Miles Per Day", "Yearly Mile Rate", "MPH", "Total Calories Burned")

kable(x = groupby_year, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```

</div>


***

# Monthly Stats

```{r echo = FALSE}
groupby_yearmonth = running %>%
  group_by(YearMonth) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            )
  )

# groupby_yearmonth$yearmonth = paste(groupby_yearmonth$Month, groupby_yearmonth$Year, sep = " ")
# groupby_yearmonth = select(as.data.frame(select(groupby_yearmonth, - Month)), - Year)
# groupby_yearmonth = groupby_yearmonth[, c(ncol(groupby_yearmonth), 1:ncol(groupby_yearmonth) - 1)]
# 
# groupby_yearmonth = rbind(groupby_yearmonth, total_row)

names(groupby_yearmonth) = c("Month", "Total Runs", "Miles", "Time", "Pace")

kable(groupby_yearmonth, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) #%>%
  #row_spec(row = nrow(groupby_yearmonth), bold = TRUE, font_size = 21)
```

```{r echo = FALSE, eval = FALSE}
ggplot(data = groupby_yearmonth, aes(x = Month, y = Miles %>% as.numeric())) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = groupby_yearmonth$Miles %>% round(digits = 2) %>% format(nsmall = 2)), vjust = 1.6, color = "white", size = 2) +
  ggtitle("Month vs. Miles") +
  theme(plot.title = element_text(hjust = 0.5))
```

<button onclick="myFunction2()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Advanced Monthly Stats </button>

<div id="myDIV2" class="collapse">  

<br />

<h3>Advanced Monthly Stats</h3>

```{r echo = FALSE}
groupby_yearmonth = running %>%
  group_by(YearMonth) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Days_Off = sum(RunDistance == 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Miles_Per_Run = miles_per_run(
              distance = RunDistance
            ),
            
            Miles_Per_Day = miles_per_day(
              distance = RunDistance %>% sum()
            ),
            
            Yearly_Mileage_Rate = yearly_mileage_pace(
              distance = RunDistance %>% sum()
            ),

            MPH = miles_per_hour(
                distance = RunDistance %>% sum(),
                minutes = RunMinutes %>% sum(),
                seconds = RunSeconds %>% sum()
            ),
            
            Calories = sum(RunCalories)
            )

names(groupby_yearmonth) = c("Month", "Total Runs", "Days Off", "Miles", "Time", "Pace", "Miles Per Run", "Miles Per Day", "Yearly Mile Rate", "MPH", "Total Calories Burned")

kable(x = groupby_yearmonth, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```

</div>

***

# Weekday Stats

```{r echo = FALSE}
groupby_weekday = running %>%
  group_by(Weekday) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            )
  )
            
            # Miles_Per_Run = floor(sum(RunDistance) * 100 / sum(RunDistance > 0)) / 100,
            
            #MPH = floor(sum(RunDistance) / (((((sum(RunMinutes) + sum(RunSeconds) %/% 60) %/% 60) * 60 * 60 + ((sum(RunMinutes) + sum(RunSeconds) %/% 60) %% 60) * 60 + sum(RunSeconds) %% 60)) / (60 * 60)) * 1000) / 1000,
            
            #Calories = sum(RunCalories)
            #)

# groupby_weekday = rbind(groupby_weekday, total_row)

names(groupby_weekday) = c("Weekday", "Total Runs", "Miles", "Time", "Pace")#, "MPH", "Calories")

# names(groupby_weekday) = c("Weekday", "Total Runs", "Distance", "Time", "Pace", "Miles Per Run", "MPH", "Calories")

kable(groupby_weekday, format = "html", align = "lrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive"))# %>%
  #row_spec(row = nrow(groupby_weekday), bold = TRUE, font_size = 21)
```

```{r echo = FALSE}
ggplot(data = groupby_weekday, aes(x = Weekday, y = Miles)) +
  geom_bar(stat = "identity", fill = "darkblue") +
  geom_text(aes(label = groupby_weekday$Miles %>% round(digits = 2) %>% format(nsmall = 2)), vjust = 1.6, color = "white", size = 5) +
  ggtitle("Weekday vs. Miles") +
  theme(plot.title = element_text(hjust = 0.5))
```

<button onclick="myFunction3()" type="button" class="btn btn-primary" data-toggle="collapse" data-target="#demo"> Click to Show Advanced Weekday Stats </button>

<div id="myDIV3" class="collapse">  

<br />

<h3>Advanced Weekday Stats</h3>

```{r echo = FALSE}
groupby_weekday = running %>%
  group_by(Weekday) %>%
  summarise(Total_Runs = sum(RunDistance > 0),
            
            Days_Off = sum(RunDistance == 0),
            
            Distance = sum(RunDistance),
            
            Time = total_time(
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Pace = pace_calculator(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Miles_Per_Run = miles_per_run(
              distance = RunDistance
            ),
            
            Miles_Per_Day = miles_per_day(
              distance = RunDistance %>% sum()
            ),
            
            Yearly_Mileage_Rate = yearly_mileage_pace(
              distance = RunDistance %>% sum()
            ),

            MPH = miles_per_hour(
              distance = RunDistance %>% sum(),
              minutes = RunMinutes %>% sum(),
              seconds = RunSeconds %>% sum()
            ),
            
            Calories = sum(RunCalories)
            )

names(groupby_weekday) = c("Weekday", "Total Runs", "Days Off", "Miles", "Time", "Pace", "Miles Per Run", "Miles Per Day", "Yearly Mile Rate", "MPH", "Total Calories Burned")

kable(x = groupby_weekday, format = "html", align = "lrrrrrrrrrrrrrr") %>%
  kable_styling(bootstrap_options = c("hover", "responsive")) %>%
  scroll_box(width = "100%", height = "100%")
```

</div>





```{r echo = FALSE, eval = FALSE}
location = running %>%
  group_by(Location) %>%
  summarise(Distance = sum(RunDistance),
            Time = sum(RunMinutes))

location = location[order(location$Distance, decreasing = TRUE), ] %>%
  head()
```















