---
title: "Kevin Wong - Trivia"
output:
  html_document:
    toc: no
---

```{r echo = FALSE, message = FALSE, warning = FALSE}
#Update_Date = as.Date("07-01-2025", format = "%m-%d-%Y")
#Update_Date

library(dplyr)
library(gghighlight)
library(ggplot2)
library(googlesheets4)
library(kableExtra)
library(knitr)
library(lubridate)
library(rlang)
library(scales)
library(shiny)
library(shinydashboard)
library(stringr)
library(tidyverse)

library(randomForest)
library(generics)
library(caret)

percent = function(x, digits = 2, format = "f", ...) {
  t = formatC(x * 100, format = format, digits = digits, ...) %>% paste("%", sep = "")
  return(t)
}

seed = 3
```

```{r echo = FALSE, message = FALSE, warning = FALSE}
gs4_deauth()

Parts = read_sheet(ss = "https://docs.google.com/spreadsheets/d/1k4vAQll8rTX4jHBNEOxlEYl1MEra502bfDBahPyEYQQ", sheet = "# of Participants")

trivia = read_sheet(ss = "https://docs.google.com/spreadsheets/d/1k4vAQll8rTX4jHBNEOxlEYl1MEra502bfDBahPyEYQQ", sheet = "Trivia Questions with Answers") %>%
  arrange(Index) %>%
  filter(`Data Version` == "C", is.na(Date) == FALSE, is.na(Category) == FALSE, is.na(TeamAnswerCorrect) == FALSE) %>%
  mutate(
    Date = Date %>% as.Date(),
    `Question Number` = `Question Number` %>% as.character() %>% as.factor(),
    Round = case_when(
      `Question Number` %in% c("1", "2", "3") ~ "1",
      `Question Number` %in% c("4", "5", "6") ~ "2",
      `Question Number` %in% c("7", "8", "9") ~ "3",
      `Question Number` %in% c("Bonus") ~ "Bonus",
      `Question Number` %in% c("Halftime") ~ "Halftime",
      `Question Number` %in% c("11", "12", "13") ~ "4",
      `Question Number` %in% c("14", "15", "16") ~ "5",
      `Question Number` %in% c("17", "18", "19") ~ "6",
      .default = `Question Number`
    ) %>% as.factor(),
    `Question within Round` = case_when(
      `Question Number` %in% c("1", "4", "7", "11", "14", "17") ~ "1",
      `Question Number` %in% c("2", "5", "8", "12", "15", "18") ~ "2",
      `Question Number` %in% c("3", "6", "9", "13", "16", "19") ~ "3",
      `Question Number` %in% c("Bonus") ~ "Bonus",
      `Question Number` %in% c("Halftime") ~ "Halftime",
      .default = `Question Number`
    ) %>% as.factor(),
    `Trivia Half` = case_when(
      Round %in% c("1", "2", "3") ~ "First Half",
      Round %in% c("4", "5", "6") ~ "Second Half",
      .default = `Question Number`
    ),
    `Correct Answer` = `Correct Answer` %>% as.character(),
    `Submitted Answer` = `Submitted Answer` %>% as.character(),
    
    Points_Wagered_Original = `Points Wagered`,
    Points_Scored_Original = case_when(
      TeamAnswerCorrect == 1  ~ Points_Wagered_Original,
      .default = 0
    ),
    Points_Wasted_Original = case_when(
      TeamAnswerCorrect == 0 ~ Points_Wagered_Original,
      .default = 0
    ),
    Points_Net_Original = case_when(
      TeamAnswerCorrect == 1 ~ Points_Wagered_Original,
      .default = - Points_Wagered_Original
    ),
    
    Points_Wagered_Weighted = case_when(
      #`Trivia Half` == "First Half" ~ Points_Wagered_Original,
      `Trivia Half` == "Second Half" & Points_Wagered_Original == "2" ~ 1,
      `Trivia Half` == "Second Half" & Points_Wagered_Original == "4" ~ 3,
      `Trivia Half` == "Second Half" & Points_Wagered_Original == "6" ~ 5,
      .default = Points_Wagered_Original
    ),
    Points_Scored_Weighted = case_when(
      TeamAnswerCorrect == 1  ~ Points_Wagered_Weighted,
      .default = 0
    ),
    Points_Wasted_Weighted = case_when(
      TeamAnswerCorrect == 0 ~ Points_Wagered_Weighted,
      .default = 0
    ),
    Points_Net_Weighted = case_when(
      TeamAnswerCorrect == 1 ~ Points_Wagered_Weighted,
      .default = - Points_Wagered_Weighted
    ),

    
    
    Category_Level02 = case_when(
      # make a grouping for business and advertising
      str_detect(string = toupper(Category), pattern = "GEOGRAPHY|PARKS|LANDMARKS") == TRUE ~ "Geography",
      str_detect(string = toupper(Category), pattern = "BASEBALL|BASKETBALL|BOWLING|BOXING|FOOTBALL|GOLF|HOCKEY|RUNNING|SOCCER|SPORTS") == TRUE ~ "Sports",
      str_detect(string = toupper(Category), pattern = "LITERATURE|BOOKS") == TRUE ~ "Literature",
      str_detect(string = toupper(Category), pattern = "HISTORY|PRESIDENTS") == TRUE ~ "History",
      str_detect(string = toupper(Category), pattern = "MOVIES|MOVIE LINES") == TRUE ~ "Movies",
      toupper(Category) == "TV" ~ "TV",
      str_detect(string = toupper(Category), pattern = "TELEVISION") == TRUE ~ "TV",
      toupper(Category) == "DOGS" ~ "Animals",
      .default = "Other"
    ),
    Category_Level03 = case_when(
      Category_Level02 == "TV" ~ 1,
      .default = 2
    ),

    Freebie = case_when(
      Freebie == 1 ~ 1,
      .default = 0
    ),
    
    TeamAnswerCorrect_Text = case_when(
      TeamAnswerCorrect == 1 ~ "Correct",
      .default = "Incorrect"
    ) %>% as.factor()
      
    ) %>%
    left_join(y = Parts, b = "Date") %>%
    select(Index, Date, `Question Number`, Round, `Question within Round`, `Trivia Half`, Category, Question, `Correct Answer`, `Submitted Answer`, TeamAnswerCorrect, Points_Wagered_Original, Points_Scored_Original, Points_Wasted_Original, Points_Net_Original, Points_Wagered_Weighted, Points_Scored_Weighted, Points_Wasted_Weighted, Points_Net_Weighted, `Question Type`, `Question Type 2`, Freebie, Notes, `Top 5 Finish`, Category_Level02, Category_Level03, NumberofTeamMembers, TeamAnswerCorrect_Text) %>%
  filter(Round %in% c("Bonus", "Halftime", "Final", "Tiebreaker") == FALSE)
```


```{r echo = FALSE, message = FALSE, warning = FALSE}
Update_Date = trivia$Date %>% as.Date() %>% max()
```


```{r echo = FALSE, message = FALSE, warning = FALSE}
#Creating Train and Test sets
set.seed(seed = seed)

trivia_trn_index = sample(x = trivia$Index, size = nrow(trivia) * .7, replace = FALSE) %>% sort(decreasing = FALSE)

trivia_tst_index = trivia %>% filter(Index %in% trivia_trn_index == FALSE) %>% select(Index) %>% unlist() %>% unname() %>% sort(decreasing = FALSE)

trivia_trn = trivia %>% filter(Index %in% trivia_trn_index)
trivia_tst = trivia %>% filter(Index %in% trivia_tst_index)

rf_fit = train(TeamAnswerCorrect ~ `Question Type` + Round + `Question within Round` + `Trivia Half` + Category + Category_Level02 + Freebie + Points_Wagered_Weighted + NumberofTeamMembers,
            data = trivia_trn,
            method = "rf",
            trControl = trainControl(method = "cv", number = 5),
            tuneLength = 5
)

rf_fit$xlevels[["Category_Level02"]] = union(rf_fit$xlevels[["Category_Level02"]], trivia_tst$Category_Level02)
rf_fit$xlevels[["Category"]] = union(rf_fit$xlevels[["Category"]], trivia_tst$Category)
rf_fit$xlevels[["Question Type"]] = union(rf_fit$xlevels[["Question Type"]], trivia_tst$`Question Type`)
rf_fit$xlevels[["Question Type 2"]] = union(rf_fit$xlevels[["Question Type 2"]], trivia_tst$`Question Type 2`)

test_data_probabilities = predict(rf_fit,  newdata = trivia_tst)

cutoffs = seq(from = 0.5, to = 1, by = 0.01)
score_acc = rep(0, length(cutoffs))

score = function(actual, predicted) {
  1   * sum(predicted == 0 & actual == 0) +
  1   * sum(predicted == 1 & actual == 1) +
  -1  * sum(predicted == 0 & actual == 1) +
  -1  * sum(predicted == 1 & actual == 0)
}

# test cutoffs for accuracy tuned forest
#for (c in test_data_probabilities) {
#  pred = ifelse(test_data_probabilities > 0.5, yes = 1, no = 0)
#}

trivia_tst$prediction_probability = test_data_probabilities
trivia_tst$prediction = case_when(
  trivia_tst$prediction_probability > 0.5 ~ 1,
  .default = 0
)

#trivia_tst$prediction = trivia_tst$prediction %>% as.factor()

trivia_tst$model_accurate = case_when(
  trivia_tst$prediction == trivia_tst$TeamAnswerCorrect ~ 1,
  .default = 0
)
```

```{r echo = FALSE, eval = FALSE}
confusionMatrix(data = rf_fit, reference = trivia_tst$TeamAnswerCorrect)
?confusionMatrix
```

```{r echo = FALSE, eval = FALSE}
print(rf_fit)

importance <- varImp(rf_fit, scale = FALSE)
plot(importance)

rpart.plot(rf_fit$finalModel, margin = 0.1)
```













<style type="text/css">
body .main-container {
	max-width: 1080px !important;
}

.left {
  text-align: left;
}

</style>



<h1>Trivia</h1>

<p class="last-updated">
Last updated: `r paste(format(x = Update_Date, format = "%B"), " ", format(x = Update_Date, format = "%d") %>% as.numeric(), ", ", format(x = Update_Date, format = "%Y") %>% as.numeric(), sep = "")`
</p>

***


<p class="left">
[Link to Google Sheets - Trivia Questions](https://docs.google.com/spreadsheets/d/1k4vAQll8rTX4jHBNEOxlEYl1MEra502bfDBahPyEYQQ){target="_blank"}
</p>



<p class="last-updated">
<!--I have been going to trivia nights with my family for about a year, and have been tracking our stats since `r paste(format(x = trivia$Date %>% min(), format = "%B"), " ", format(x = trivia$Date %>% min(), format = "%d") %>% as.numeric(), ", ", format(x = trivia$Date %>% min(), format = "%Y") %>% as.numeric(), sep = "")`.
-->
Team Answer Correct: `r paste(trivia$TeamAnswerCorrect %>% mean() %>% percent(), sep = "")`<br />
Random Forest: `r paste(trivia_tst$model_accurate %>% mean() %>% percent(), sep = "")`
</p>

<p class="last-updated">
At trivia night, my family answers about `r paste(trivia$TeamAnswerCorrect %>% mean() %>% percent(), sep = "")` of questions accurately.
<br />
However, using a Random Forest model, I can predict whether we got it correct or not with an accuracy of `r paste(trivia_tst$model_accurate %>% mean() %>% percent(), sep = "")`.
</p>

***

Example:
Training Data
```{r echo = FALSE, message = FALSE, warning = FALSE}
set.seed(seed = seed)
Table_Train_Int = sample(x = trivia_trn_index, size = 20, replace = FALSE)
Table_Train_Sample = trivia_trn %>%
  filter(Index %in% Table_Train_Int) %>%
  select(Date, Category, `Question Type`, Freebie, NumberofTeamMembers, TeamAnswerCorrect_Text) %>%
  arrange(Date, Category, `Question Type`, Freebie, NumberofTeamMembers, TeamAnswerCorrect_Text)

names(Table_Train_Sample) = c("Date", "Category", "Question Type", "Freebie", "Team Members", "Team Answer Correct")

kable(Table_Train_Sample, format = "html", align = "llllll") %>%
  kable_styling(bootstrap_options = c("responsive"), full_width = TRUE) %>%
  column_spec(column = c(1:ncol(Table_Train_Sample)), background = "white", color = "black", include_thead = TRUE)
```

Example:
Testing Data
```{r echo = FALSE, message = FALSE, warning = FALSE}
set.seed(seed = seed)
Table_Test_Int = sample(x = trivia_tst_index, size = 10, replace = FALSE)
Table_Test_Sample = trivia_tst %>%
  filter(Index %in% Table_Test_Int) %>%
  mutate(
    ModelPredictionTeamAnswer  = ifelse(prediction == 1, "Correct", "Incorrect"),
    ModelPredictionProbability = prediction_probability %>% percent(),
    ModelPredictionAccuracy    = ifelse(model_accurate == 1, "Accurate", "Inaccurate")
  ) %>%
  select(Date, Category, `Question Type`, Freebie, NumberofTeamMembers, TeamAnswerCorrect_Text, ModelPredictionTeamAnswer, ModelPredictionProbability, ModelPredictionAccuracy) %>%
  arrange(Date, Category, `Question Type`, Freebie, NumberofTeamMembers, TeamAnswerCorrect_Text, ModelPredictionTeamAnswer, ModelPredictionProbability, ModelPredictionAccuracy)

names(Table_Test_Sample) = c("Date", "Category", "Question Type", "Freebie", "Team Members", "Team Answer Correct", "Model Prediction of Team Answer", "Model Prediction Probability", "Model Prediction Accuracy")

kable(Table_Test_Sample, format = "html", align = "lllllllll") %>%
  kable_styling(bootstrap_options = c("responsive"), full_width = TRUE) %>%
  column_spec(column = c(1:ncol(Table_Test_Sample)), background = "white", color = "black", include_thead = TRUE) %>%
  column_spec(column = ncol(Table_Test_Sample), background = case_when(Table_Test_Sample$`Model Prediction Accuracy` == "Accurate" ~ "green", .default = "red"), include_thead = FALSE)
```


***

<p class="left">
[Link to Shiny App](https://kevinjameswong.shinyapps.io/trivia/){target="_blank"}
</p>


<div class="shiny-container">
<iframe src="https://kevinjameswong.shinyapps.io/trivia/">
</iframe>
</div>



```{r echo = FALSE, eval = FALSE, message = FALSE, warning = FALSE}
rfImp = varImp(rf_fit, scale = FALSE)
rfImp


Also make something that has accuracy of model across time
```







